Topic modeling on EU and the USA research projects

### 2017-06-20 thesis_report/draft_thesis.tex
Appendix wordclouds (2/10)

\begin{center}
\begin{figure}
\begin{tabular}{rcl}
\subfloat[Topic 0]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/eu_topics/eu_FP4_wordclouds/EUFP4_topic0_7000.png}} &
\subfloat[Topic 1]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/eu_topics/eu_FP4_wordclouds/EUFP4_topic1_7000.png}}&
\subfloat[Topic 2]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/eu_topics/eu_FP4_wordclouds/EUFP4_topic2_7000.png}}\\
\subfloat[Topic 3]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/eu_topics/eu_FP4_wordclouds/EUFP4_topic3_7000.png}}&
\subfloat[Topic 4]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/eu_topics/eu_FP4_wordclouds/EUFP4_topic4_7000.png}} &
\subfloat[Topic 5]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/eu_topics/eu_FP4_wordclouds/EUFP4_topic5_7000.png}}\\
\subfloat[Topic 6]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/eu_topics/eu_FP4_wordclouds/EUFP4_topic6_7000.png}} &
\subfloat[Topic 7]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/eu_topics/eu_FP4_wordclouds/EUFP4_topic7_7000.png}}&
\subfloat[Topic 8]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/eu_topics/eu_FP4_wordclouds/EUFP4_topic8_7000.png}}\\
\subfloat[Topic 9]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/eu_topics/eu_FP4_wordclouds/EUFP4_topic9_7000.png}}&
\end{tabular}
\caption{Wordclouds of topics of the EU FP4 (1994-1998)}
\end{figure}
\end{center}

\begin{center}
\begin{figure}
\begin{tabular}{rcl}
\subfloat[Topic 0]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/eu_topics/eu_FP5_wordclouds/EUFP5_topic0_7000.png}} &
\subfloat[Topic 1]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/eu_topics/eu_FP5_wordclouds/EUFP5_topic1_7000.png}}&
\subfloat[Topic 2]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/eu_topics/eu_FP5_wordclouds/EUFP5_topic2_7000.png}}\\
\subfloat[Topic 3]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/eu_topics/eu_FP5_wordclouds/EUFP5_topic3_7000.png}}&
\subfloat[Topic 4]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/eu_topics/eu_FP5_wordclouds/EUFP5_topic4_7000.png}} &
\subfloat[Topic 5]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/eu_topics/eu_FP5_wordclouds/EUFP5_topic5_7000.png}}\\
\subfloat[Topic 6]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/eu_topics/eu_FP5_wordclouds/EUFP5_topic6_7000.png}} &
\subfloat[Topic 7]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/eu_topics/eu_FP5_wordclouds/EUFP5_topic7_7000.png}}&
\subfloat[Topic 8]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/eu_topics/eu_FP5_wordclouds/EUFP5_topic8_7000.png}}\\
\subfloat[Topic 9]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/eu_topics/eu_FP5_wordclouds/EUFP5_topic9_7000.png}}&
\end{tabular}
\caption{Wordclouds of topics of the EU FP5 (1998-2002)}
\end{figure}
\end{center}

>>>>

\begin{center}
\begin{figure}
\begin{tabular}{rcl}
\subfloat[Quality Management Systems]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/eu_topics/eu_FP4_wordclouds/EUFP4_topic0_7000.png}} &
\subfloat[Agriculture, Fisheries and Food]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/eu_topics/eu_FP4_wordclouds/EUFP4_topic1_7000.png}}&
\subfloat[Molecular biology, Genetics]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/eu_topics/eu_FP4_wordclouds/EUFP4_topic2_7000.png}}\\
\subfloat[EU transport]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/eu_topics/eu_FP4_wordclouds/EUFP4_topic3_7000.png}}&
\subfloat[Digital systems]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/eu_topics/eu_FP4_wordclouds/EUFP4_topic4_7000.png}} &
\subfloat[Materials processing]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/eu_topics/eu_FP4_wordclouds/EUFP4_topic5_7000.png}}\\
\subfloat[Genetics]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/eu_topics/eu_FP4_wordclouds/EUFP4_topic6_7000.png}} &
\subfloat[Policy for environmental sustainability]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/eu_topics/eu_FP4_wordclouds/EUFP4_topic7_7000.png}}&
\subfloat[Energy technologies]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/eu_topics/eu_FP4_wordclouds/EUFP4_topic8_7000.png}}\\
\subfloat[Applications in mobile networks]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/eu_topics/eu_FP4_wordclouds/EUFP4_topic9_7000.png}}&
\end{tabular}
\caption{Wordclouds of topics of the EU FP4 (1994-1998)}
\end{figure}
\end{center}

\begin{center}
\begin{figure}
\begin{tabular}{rcl}
\subfloat[Management software]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/eu_topics/eu_FP5_wordclouds/EUFP5_topic0_7000.png}} &
\subfloat[Hydropower / Energy production]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/eu_topics/eu_FP5_wordclouds/EUFP5_topic1_7000.png}}&
\subfloat[Information technologies]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/eu_topics/eu_FP5_wordclouds/EUFP5_topic2_7000.png}}\\
\subfloat[Quality control systems]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/eu_topics/eu_FP5_wordclouds/EUFP5_topic3_7000.png}}&
\subfloat[Healthcare / Medical genetics]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/eu_topics/eu_FP5_wordclouds/EUFP5_topic4_7000.png}} &
\subfloat[Environmental sustainability and policies]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/eu_topics/eu_FP5_wordclouds/EUFP5_topic5_7000.png}}\\
\subfloat[Molecular biology (genes)]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/eu_topics/eu_FP5_wordclouds/EUFP5_topic6_7000.png}} &
\subfloat[Optical quantum computing]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/eu_topics/eu_FP5_wordclouds/EUFP5_topic7_7000.png}}&
\subfloat[Education in Nuclear physics]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/eu_topics/eu_FP5_wordclouds/EUFP5_topic8_7000.png}}\\
\subfloat[Education, training]{\includegraphics[width=0.35\textwidth, natwidth=640,natheight=480]{figs/eu_topics/eu_FP5_wordclouds/EUFP5_topic9_7000.png}}&
\end{tabular}
\caption{Wordclouds of topics of the EU FP5 (1998-2002)}
\end{figure}
\end{center}
